\documentclass[letterpaper,12pt]{article}[leftmargin=*]

\usepackage[empty]{fullpage}
\usepackage{enumitem}
\usepackage{ifxetex}
\ifxetex
  \usepackage{fontspec}
  \usepackage[xetex]{hyperref}
\else
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
  \usepackage[pdftex]{hyperref}
\fi
\usepackage{fontawesome}
\usepackage[sfdefault,light]{FiraSans}
\usepackage{anyfontsize}
\usepackage{xcolor}
\usepackage{tabularx}

%-------------------------------------------------- SETTINGS HERE --------------------------------------------------
% Header settings
\def \fullname {Bo HAN}
\def \subtitle {}

\def \linkedinicon {\faLinkedin}
\def \linkedinlink {https://linkedin.com/in/hanbo/}
\def \linkedintext {/hanbo}

\def \phoneicon {\faPhone}
\def \phonetext {+61-425-719-696}

\def \emailicon {\faEnvelope}
\def \emaillink {mailto:tq010or@gmail.com}
\def \emailtext {TQ010OR@gmail.com}

\def \githubicon {\faGithub}
\def \githublink {https://github.com/tq010or}
\def \githubtext {/TQ010OR}

\def \websiteicon {\faGlobe}
\def \websitelink {http://tq010or.github.io/}
\def \websitetext {Website}

\def \headertype {\doublecol} % \singlecol or \doublecol

% Misc settings
\def \entryspacing {-0pt}

\def \bulletstyle {\faAngleRight}

% Define colours
\definecolor{primary}{HTML}{000000}
\definecolor{secondary}{HTML}{0D47A1}
\definecolor{accent}{HTML}{263238}
\definecolor{links}{HTML}{1565C0}

%------------------------------------------------------------------------------------------------------------------- 

% Defines to make listing easier
\def \linkedin {\linkedinicon \hspace{3pt}\href{\linkedinlink}{\linkedintext}}
\def \phone {\phoneicon \hspace{3pt}{ \phonetext}}
\def \email {\emailicon \hspace{3pt}\href{\emaillink}{\emailtext}}
\def \github {\githubicon \hspace{3pt}\href{\githublink}{\githubtext}}
\def \website {\websiteicon \hspace{3pt}\href{\websitelink}{\websitetext}}

% Adjust margins
\addtolength{\oddsidemargin}{-0.55in}
\addtolength{\evensidemargin}{-0.55in}
\addtolength{\textwidth}{1.1in}
\addtolength{\topmargin}{-0.6in}
\addtolength{\textheight}{1.1in}

% Define the link colours
\hypersetup{
    colorlinks=true,
    urlcolor=links,
}

% Set the margin alignment 
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%-------------------------
% Custom commands

% Sections
\renewcommand{\section}[2]{\vspace{5pt}
  \colorbox{secondary}{\color{white}\raggedbottom\normalsize\textbf{{#1}{\hspace{7pt}#2}}}
}

% Entry start and end, for spacing
\newcommand{\resumeEntryStart}{\begin{itemize}[leftmargin=2.5mm]}
\newcommand{\resumeEntryEnd}{\end{itemize}\vspace{\entryspacing}}

% Itemized list for the bullet points under an entry, if necessary
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=4.5mm]}
\newcommand{\resumeItemListEnd}{\end{itemize}}

% Resume item
\renewcommand{\labelitemii}{\bulletstyle}
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

% Entry with title, subheading, date(s), and location
\newcommand{\resumeEntryTSDL}[4]{
  \vspace{-1pt}\item[]
    \begin{tabularx}{0.97\textwidth}{X@{\hspace{60pt}}r}
      \textbf{\color{primary}#1} & {\firabook\color{accent}\small#2} \\
      \textit{\color{accent}\small#3} & \textit{\color{accent}\small#4} \\
    \end{tabularx}\vspace{-6pt}
}

% Entry with title and date(s)
\newcommand{\resumeEntryTD}[2]{
  \vspace{-1pt}\item[]
    \begin{tabularx}{0.97\textwidth}{X@{\hspace{60pt}}r}
      \textbf{\color{primary}#1} & {\firabook\color{accent}\small#2} \\
    \end{tabularx}\vspace{-6pt}
}

% Entry for special (skills)
\newcommand{\resumeEntryS}[2]{
  \item[]\small{
    \textbf{\color{primary}#1 }{ #2 \vspace{-6pt}}
  }
}

% Double column header
\newcommand{\doublecol}[6]{
  \begin{tabularx}{\textwidth}{Xr}
    {
      \begin{tabular}[c]{l}
        \fontsize{35}{45}\selectfont{\color{primary}{{\textbf{\fullname}}}} \\
        {\textit{\subtitle}} % You could add a subtitle here
      \end{tabular}
    } & {
      \begin{tabular}[c]{l@{\hspace{1.5em}}l}
        {\small#4} & {\small#1} \\
        {\small#5} & {\small#2} \\
        {\small#6} & {\small#3}
      \end{tabular}
    }
  \end{tabularx}
}

% Single column header
\newcommand{\singlecol}[6]{
  \begin{tabularx}{\textwidth}{Xr}
    {
      \begin{tabular}[b]{l}
        \fontsize{35}{45}\selectfont{\color{primary}{{\textbf{\fullname}}}} \\
        {\textit{\subtitle}} % You could add a subtitle here
      \end{tabular}
    } & {
      \begin{tabular}[c]{l}
        {\small#1} \\
        {\small#2} \\
        {\small#3} \\
        {\small#4} \\
        {\small#5} \\
        {\small#6}
      \end{tabular}
    }
  \end{tabularx}
}

\begin{document}
%-------------------------------------------------- BEGIN HERE --------------------------------------------------

%---------------------------------------------------- HEADER ----------------------------------------------------

\headertype{\linkedin}{\github}{\website}{\phone}{\email}{} % Set the order of items here
\vspace{-10pt} % Set a negative value to push the body up, and the opposite

%-------------------------------------------------- Statement --------------------------------------------------
\section{\faFlask}{Personal Statement}

    \resumeItemListStart
      \resumeItem {I am a problem solver and capability enabler with R\&D and consulting experience in media, telco, health and financial services. My analytical mindset, agile prototyping skills, team leadership, product and programme delivery experience enable me to develop impact-oriented solutions for business value creations.}
    \resumeItemListEnd

%-------------------------------------------------- EXPERIENCE --------------------------------------------------
\section{\faPieChart}{Work Experience}

  \resumeEntryStart
    \resumeEntryTSDL
      {Accenture}{Sep 2018 -- Present}
      {Delivery Lead/Data Engineer Manager}{Sydney, Australia}
    \resumeItemListStart
      \resumeItem {Led the new platform design and data migration for a client's business critical legacy system}
      \resumeItem {Oversaw tech architecture design and implementation for a client's 5G roll-out}
      \resumeItem {Set up and improved process, culture and capability for a diverse team as a delivery lead}
      \resumeItem {Coordinated business units and tech teams to unblock barriers and ensure shared goals}
      \resumeItem {Brought next best actions and improvement plans for managements in quarterly roadmap plannings.}
    \resumeItemListEnd
  \resumeEntryEnd

  \resumeEntryStart
    \resumeEntryTSDL
      {Kaplan}{May 2017 -- Aug 2018}
      {NLP Specialist}{Sydney, Australia}
    \resumeItemListStart
      \resumeItem {Optimised a text-based financial compliance system with more than 100x speed up.} 
      \resumeItem{Drove a serverless design in cloud which significantly boosted the system throughput and scalability.}
      \resumeItem {Applied active learning and other pragmatic methods to improve compliance system accuracy.}
      \resumeItem {Co-developed an in-house data anonymisation system for personal and identifiable information.}
    \resumeItemListEnd
  \resumeEntryEnd

  \resumeEntryStart
    \resumeEntryTSDL
      {Hugo AI (Sydney Startup)}{Mar 2016 -- Mar 2017}
      {Data Scientist}{Sydney, Australia}
    \resumeItemListStart
        \resumeItem {Designed and implemented an automatic user profile summarisation system. The work features data crawling, cleaning, reconciliation and natural language generation from various social media sources. The deliverables facilitate online recruiters for more effective and efficient talent acquisitions.}
    \resumeItemListEnd
  \resumeEntryEnd

  \resumeEntryStart
    \resumeEntryTSDL
      {IBM Research}{Apr 2014 -- Mar 2016}
      {Research Scientist}{Melbourne, Australia}
    \resumeItemListStart
      \resumeItem {Led the design and implementation for a number of social media analytics with ML and NLP, including (a) a text-based \href{http://researcher.watson.ibm.com/researcher/view_group.php?id=6349}{geotagger}, (b) \href{http://researcher.watson.ibm.com/researcher/view_group.php?id=6350}{Social Media Analytics in Real Time} and (c) a biomedical \href{http://researcher.watson.ibm.com/researcher/view_group_pubs.php?grp=5727}{named entity recogniser}. The deliverables have been utilised by clients from fashion, sports and insurance.}
    \resumeItemListEnd
  \resumeEntryEnd

  \resumeEntryStart
    \resumeEntryTSDL
      {Melbourne University/NICTA}{Jul 2010 -- Mar 2014}
      {PhD and Research Assistant}{Melbourne, Australia}
    \resumeItemListStart
      \resumeItem {Applied NLP/ML methods to improve the utility of social media for various analytics, including "\href{http://research.unimelb.edu.au/__data/assets/pdf_file/0006/1891914/IBES-2012-Annual-Report.pdf}{Early detection and mitigation of disastrous events with broadband-enabled social interaction technologies}".}
    \resumeItemListEnd
  \resumeEntryEnd

  \resumeEntryStart
    \resumeEntryTSDL
      {Microsoft Research Asia}{Jan 2007 -- Aug 2007, Sep 2009 -- Jun 2010}
      {Fulltime Research Intern}{Beijing, China}
    \resumeItemListStart
      \resumeItem {Co-developed an English writing assistant which has been productised as \href{https://www.bing.com/dict?FORM=Z9LH3}{Bing Search Dictionary} in China. My work includes bilingual text mining, short sentence categorisation, incremental bilingual text crawling. This product had won \href{https://www.wsj.com/articles/SB10001424052748703545604575406771145298614}{2010 Wall Street Journal Asian Innovation Award}.}
    \resumeItemListEnd
  \resumeEntryEnd

%-------------------------------------------------- SKILLS --------------------------------------------------
\section{\faGears}{Professional Skills}
 \resumeEntryStart
  \resumeEntryS{Cloud} {(a) best practise for multi-tier scalable and reliable solutions; (b) design for high availability and disaster recovery; (c) serverless/containerisation architecture; (d) complex programme delivery; (e) data migration and integration; (f) enterprise hybrid solutions}
  \resumeEntryS{Frontend} {HTML, CSS, Javascript (JQuery, Vue and React)}
  \resumeEntryS{Programming} {Python, R, Bash, Java, C\#, C/C++}
  \resumeEntryS{Modelling} {Jupyter, pandas, scikit-learn, spaCy, word2vec, PyTorch, transformers, AWS SageMaker}
  \resumeEntryS{Backend} {MySQL, Postgres, Redis/Memcached, Kafka, MongoDB}
  \resumeEntryS{Container/DevOps} {Docker, Kubernetes/OpenShift, git/bitbucket, JIRA/Trello, Jenkisn/Bamboo}
 \resumeEntryEnd

%-------------------------------------------------- SKILLS --------------------------------------------------
\section{\faGears}{General Skills}

 \resumeEntryStart
  \resumeEntryS{Management, Leadership and Communications}{
   \resumeItemListStart
      \resumeItem {Identify high-value opportunities from business context, and map ideas into products and services}
      \resumeItem {Deliver objectives and impact-oriented solutions with best practise}
      \resumeItem {Enable data analytics capability from scratch for a practise}
      \resumeItem {Manage stakeholder expectations and come up with plans for next best moves}
      \resumeItem {Coordinate across business functions and work as a team}
      \resumeItem {Present to diverse audiences, e.g., invited talks in universities, showcases for partners and clients}
    \resumeItemListEnd}
  \resumeEntryS{Language} {English (professional), Mandarin (native), Japanese (learner)}
 \resumeEntryEnd

%-------------------------------------------------- EDUCATION --------------------------------------------------
\section{\faGraduationCap}{Education}

  \resumeEntryStart
    \resumeEntryTSDL
      {Melbourne University}{2010 -- 2014}
      {PhD in Computer Science (Natural Language Processing)}{Melbourne, Australia}
    \resumeEntryTSDL
      {Dalian University of Technology}{2003 -- 2009}
      {Bachelor and Master in Software Engineering}{Dalian, China}
  \resumeEntryEnd

%-------------------------------------------------- Extra --------------------------------------------------
\section{\faGears}{Extra Information}

 \resumeEntryStart
  \resumeEntryS{My research}{focuses on \href{https://minerva-access.unimelb.edu.au/bitstream/handle/11343/41029/thesis.pdf?sequence=1}{Improving the Utility of Social Media with Natural Language Processing}. In particular, I studied Twitter text normalisation and geolocation prediction in depth. A tweet length summary of this work is \textit{U wanto undrstnd TWEETS lik dis? Make them readable like this; and if there are too many to read, select those from a region.}}
\resumeEntryS{Professional achievements}{
    \resumeItemListStart
      \resumeItem {Certified \href{https://www.youracclaim.com/badges/c7ac42bd-fe9a-4f13-83b3-80cea3a8cc57/public_url}{AWS Solution Architect Associate} and \href{https://www.youracclaim.com/badges/f7d5a6a9-caaf-472c-b703-207ae1046147/public_url}{Professional}}
      \resumeItem {Published a few top-tier conference and journal papers (e.g. ACL, EMNLP, COLING and JAIR). My H10-index is 15 and the most cited paper is over 500 (by 2020). See \href{https://scholar.google.com/citations?hl=en&user=ZRr4vn8AAAAJ}{Google Scholar} for a full list of publications.}
      \resumeItem {Co-organised two international workshops on social media analytics (\href{https://noisy-text.github.io/2015/}{W-NUT 2015} and \href{https://noisy-text.github.io/2015/}{W-NUT 2016}).}
      \resumeItem {Held two issued patents in the United States (US9569551B2, US9697245B1).}
      \resumeItem {Held one software copyright in China (2015SR225534).}
    \resumeItemListEnd}

  \resumeEntryS{Projects} {I like coding side projects for fun. They are like Unix utilities dedicated to solve a particular pain point. The most recent one is \href{https://panda-lens.com/}{panda-lens.com}. It is a pure data-driven real-time trend analysis platform.}
  \resumeEntryS{Hobbies} {Cook gourmet food daily; Play badminton weekly; Travel 3 times a year; Had one detective novel (written in Mandarin)}
 \resumeEntryEnd


\end{document}
